Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spanning 500\,Parsecs

### 2021-03-16 cluster_paper/ms.tex
update ms

The detection of dispersed stellar associations, although possible
before Gaia, has now reached a breakthrough pace \citep[{\it
e.g.},][]{bergond_gravitational_2001,zuckerman_young_2004,oh_comoving_2017,cantatgaudin_gaia_2018,gagne_banyan_XII_2018,gagne_banyan_XIII_2018,kounkel_apogee2_2018,zari_3d_2018,kounkel_untangling_2019,furnkranz_comabernbhr_2019}.
The populations found by these studies can be summarized as follows.
On one end are coeval groups with no discernable cores ({\it e.g.},
Psc Eri and $\mu$ Tau,
\citealt{meingast_psceri_2019,curtis_tess_2019,gagne_mutau_2020}).  On
the other are hierarchically structured associations with many over
and under-densities  \citep[{\it e.g.} the Sco-Cen and Vela
associations][]{pecaut_star_2016,cantatgaudin_velaOB2_2019}.  Here, we focus on
an intermediate regime: low-density halos associated with a single
overdensity, typically an open cluster that was known before Gaia
\citep[see][]{kounkel_untangling_2019,kounkel_untanglingII_2020,meingast_2021}.
In some cases, these halos could correspond to tidal tails, as have
been reported in the Hyades
\citep{meingast_hyades_2019,roser_hyades_2019}, the Ursa Major moving
group \citep{gagne_lowmassUMA_2020}, and in Coma Berenices
\citep{tang_comaber_2019}.

@@

A second explanation though invokes
the idea that the cluster formed in a larger and lower-density star
formation complex, and the stars we see in the halo did not in fact
form in say the same ``clump'' as those in the cluster core.

>>>>

The detection of dispersed stellar associations, although possible
before Gaia, has now reached a breakthrough pace \citep[{\it
e.g.},][]{de_zeeuw_hipparcos_1999,bergond_gravitational_2001,zuckerman_young_2004,oh_comoving_2017,cantatgaudin_gaia_2018,gagne_banyan_XII_2018,gagne_banyan_XIII_2018,kounkel_apogee2_2018,zari_3d_2018,kounkel_untangling_2019,furnkranz_comabernbhr_2019}.
The populations found by these studies can be summarized as follows.
On one end are coeval groups with no discernable cores ({\it e.g.},
Psc Eri and $\mu$ Tau,
\citealt{meingast_psceri_2019,curtis_tess_2019,gagne_mutau_2020}).  On
the other are hierarchically structured associations with many over
and under-densities  \citep[{\it e.g.} the Sco-Cen and Vela
associations][]{pecaut_star_2016,cantatgaudin_velaOB2_2019}.  Here, we focus on
an intermediate regime: low-density halos associated with a single
overdensity, typically an open cluster that was known before Gaia
\citep[see][]{kounkel_untangling_2019,kounkel_untanglingII_2020,meingast_2021}.
In some cases, these halos could correspond to tidal tails, as have
been reported in the Hyades
\citep{meingast_hyades_2019,roser_hyades_2019}, the Ursa Major moving
group \citep{gagne_lowmassUMA_2020}, and in Coma Berenices
\citep{tang_comaber_2019}.

@@

A second explanation though invokes
the idea that the cluster formed in a larger and lower-density star
formation complex, and the stars we see in the halo did not in fact
form the same ``clump'' as those in the cluster core.

Consider for instance the Orion\,A cloud.  \citet{grosschedl_3d_2018} showed
using YSOs that formed in the past few megayears as tracers that Orion\,A is
best described with two components:
a dense ``head'', and a lower density 75\,pc long ``tail''.
While this filament currently totals 90\,pc in length, its future evolutionary state could very well resemble something like \cn.
A direct numerical exploration would be necessary to be sure {\bf FIXME}.

CITE ALSO: ZUCKER 2017 BONES CATALOG.

CITE ALSO: WRIGHT+2016, WRIGHT AND MAMAJEK 2018 -- LOOKED AT SCO CEN, FOUND
THAT THEY DIDN'T COME FROM A SINGLE CLUSTER BEING DISRUPTED, BUT WERE MORE
LIKELY EXPLAINED THROUGH ``EXTENDED'' STAR FORMATION OVER A MUCH LARGER VOLUME.

Similarly Zari et al 2019 studied the entire Orion complex, and found that
different regions of the complex (one toward the Belt, one toward 25\,Ori)
began forming stars roughly simultaneously. No evidence was found of it
propagating from these initial sites.

ARE THE MOLECULAR CLOUDS THEMSELVES STRUCTURED INTO CORES AND TAILS?

cometary-like cloud,
oriented toward the Galactic plane, with two distinct components:
a denser and enhanced star-forming (bent) Head, and a
lower density and star-formation quieter 75 pc long Tail.
